---
title: "Assignment 5"
author: "Shubham Bhargava"
date: "2023-10-28"
output: html_document
---

```{r}

library(fpp)
library(fpp2)
library(TTR)
library(readxl)

# Reading Data 

dataframe <- read_excel("C:/Users/Student/Desktop/BF/Sunspots.xlsx")

# Converting to Time Series Data 

Time_series= ts(dataframe$`Monthly Mean Total Sunspot Number`, start = c(2013,01),end= c (2020,12),frequency = 12)
Time_series

# Attributes and Structure

attributes(Time_series)
str(Time_series) 

```

# Decomposition 

## Seasonal Decomposition of Time Series by Loess (STL) Method

```{r}

head(Time_series)
plot(Time_series)
stl_decomp <- stl(Time_series,s.window ="periodic")
plot(stl_decomp)
attributes(stl_decomp)

```

# Taking out Seasonal Adjustment 

```{r}

seasadj(stl_decomp)

```

# Plot a line on the graph

```{r}

plot(Time_series)
lines(seasadj(stl_decomp), col= "Red")

```

# Default period forecast

```{r}

Time_series_forecast <- forecast(stl_decomp)

```
# Forecasting the Seasonally Adjusted Decomposed Time Series

```{r}
Time_series_forecast <- forecast(stl_decomp,h=20)
plot(Time_series_forecast)

```

## Plotting the seasonal component

```{r}

plot(stl_decomp$time.series[, "seasonal"], main="Seasonal Component")

```

## Plotting the trend component

```{r}

plot(stl_decomp$time.series[, "trend"], main="Trend Component")

```

## Plotting the remainder component
```{r}

plot(stl_decomp$time.series[, "remainder"], main="Remainder (Residual) Component")

```

# Other Method Of Decomposition

```{r}

decomp_elec <- decompose(Time_series)
plot(decomp_elec)

```


# Each one shows different attributes 

```{r}

attributes(decomp_elec)
seasadj(decomp_elec)

```


## Using Decompose Function

```{r}

Time_series_decompose <- decompose(Time_series)
attributes(Time_series_decompose)
plot(Time_series_decompose)


```

# Seasonal Adjustment

```{r}
Time_series_decompose_seasadj = seasadj(Time_series_decompose)
plot(Time_series_decompose_seasadj)

```

# Plotting Line Seasonally Adjusted Decomposed TS with the original Time Series

```{r}

plot(Time_series)
lines(Time_series_decompose_seasadj, col="green")





